Datasheet for 'Donor Preferences in Canadian Political Financing

### 2024-12-19 other/datasheet/datasheet.qmd
Updated datasheet

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of Australian politicians. We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The Investigative Journalism Foundation created the dataset, they are an independent organization.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The IJF is funded by several foundations: Mitacs, Social Sciences and Humanities Research Council, 3858278 Canada Foundation, Canadian Internet Registration Authority, Data Driven Reporting Project, Avanti Foundation, Balsillie Family Foundation, C4C Canada, Data Science For Social Good, Toronto Metropolitan University and Individuals.
4. *Any other comments?*
    - NA

>>>>

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to analyze political donations in Canada, specifically to investigate whether the status of a political party, being in power or not, affects the level of donations it receives.   
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The Investigative Journalism Foundation created the dataset, they are an independent organization.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The IJF is funded by several foundations: Mitacs, Social Sciences and Humanities Research Council, 3858278 Canada Foundation, Canadian Internet Registration Authority, Data Driven Reporting Project, Avanti Foundation, Balsillie Family Foundation, C4C Canada, Data Science For Social Good, Toronto Metropolitan University and Individuals.
4. *Any other comments?*
    - NA
